% !TEX program = xelatex
% This is my resume
% by ice1000

\documentclass{resume}

\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{linespacing_fix} % disable extra space before next section

\begin{document}
\pagestyle{fancy}
\fancyhf{}
\renewcommand\headrulewidth{0pt}
\cfoot{\thepage\ of \pageref{LastPage}}

\name{Tesla Ice Zhang}

\basicInfo{
  \email{ice1000kotlin@foxmail.com} \textperiodcentered\
  \phone{(+86) 180-8192-5082} \textperiodcentered\
  \github[ice1000]{https://github.com/ice1000}
  % \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The Pennsylvania State University (PSU)}, PA, US}{08/18 -- Current}
  Major: Computer Science, Anticipated Graduation Date: 06/22

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Sourcebrella Inc.}, Shenzhen, China}{02/18 -- 07/18}
\role{Intern}{Compiler Front-End, IDE Plugin Development}
\begin{itemize}
  \item Created IntelliJ/CLion/Eclipse plugin of the Pinpoint analyzer. Helped create SonarQube plugin.
  \item Created a multi-threading cross Java/Kotlin source code indexer which index Hadoop in 4 minutes.
  \item Learned a lot about Linux programming and clang/llvm.
\end{itemize}

\datedsubsection{\textbf{PingCAP}, Remote}{08/18 -- Current}
\role{Intern}{TiKV Team}
\begin{itemize}
  \item Improved many libraries used by TiKV. For example,
    optimized the memory performance of
    \href{https://docs.rs/crate/grpcio} {grpcio},
    and added new features to
    \href{https://docs.rs/crate/procinfo} {procinfo}.
\end{itemize}

\section{\faGithubAlt\ Personal Projects}
% \datedsubsection{\textbf{FriceEngine}}{\url{https://icela.github.io/}}
% % \role{Kotlin, C\#, Racket, Ruby}{Founder and main contributer to the Kotlin/C\#/Ruby version}
% A multilingual, natively-written, easy-to-use game engine series.
% \begin{itemize}
%   \item Based on life cycle / utility APIs, based on each languages' built-in GUI framework,
%     easy to install.
%   \item GitHub issues / milestones are used as task / version managing tools, nice changelogs.
%   \item A JavaFX-based drag-and-drop GUI designer, generates multilingual codes for each language.
% \end{itemize}
\datedsubsection{\textbf{DevKt}}{\url{https://github.com/ice1000/dev-kt}}
Cross-platform lightweight code editor / Kotlin IDE
\begin{itemize}
  \item Built-in Java/Kotlin highlights and completion, that can support other languages
    via plugins (transplantable from JetBrains IDE's).
    Has extra build \& run support for Kotlin.
  \item Flexible architecture, decoupled high-level logic with UI, migration to other UI frameworks is easy.
  \item Provides fine-grained highlight color and keymap settings, supports hot reload.
\end{itemize}

\datedsubsection{\textbf{Lice language}}{\url{https://github.com/lice-lang/lice}}
% \role{Kotlin, Java}{Founder and main contributer}
Scalable programming language running on JVM
\begin{itemize}
  \item Supports lambda with and lazy (call by need)/macro (call by name)/strict (call by value).
  \item About 1/20 of Java's (Hotspot 8u151) performance, provides Java interaction and script engine support.
  \item Provides CLI REPL with GHCi-style code completion/colored output and JetBrains.
    IDE plugin supporting semantic-based highlights, completion, go-to-definition, rename, eval-and-replace, quick fixes, etc.
\end{itemize}

\datedsubsection{\textbf{Julia-IntelliJ}}{\url{https://github.com/ice1000/julia-intellij}}
Julia plugin for JetBrains IDEs, compatible with all JetBrains Products.
\begin{itemize}
  \item Semantic-based highlighting, quick fixes, completion, parameter hint, special input mode for Unicode characters.
  \item Use Markdown plugin to highlight doc strings, provides REPL and SciView (showing the output of Plot libraries).
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

%% \section{\faHeartO\ Achievements}
%% \datedline{}{Aug. 2017}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.25ex]
  \item \textbf{Programming Languages}:
    \textbf{multilingual developer} (not limited to any specific language),
    and especially experienced in Java/Kotlin/Rust/C\#/Agda/Haskell,
    comfortable with Dart/C++/F\#/F$\star$ (listed in random order).

  % compiler theories
  \item \textbf{Compilers}:
    familiar with various Parser Generators/Combinators,
    understand CPS and ANF, studied some
    theories about dependent types (like Luo's UTT, Martin-Löf Type Theory)
    and their implementations in programming languages.

  % language Kotlin
  \item \textbf{Kotlin/Java}:
    \textbf{2 years} of experience,
    \textbf{4} projects collected in
    \href{https://kotlin.link/?q=ice} {Awesome Kotlin},
    familiar with JNI programming, the Gradle build tool, have experience
    in using the Kotlin compiler to analyze Java code.

  \item \textbf{Formal Verification}:
    understand dependent types / (co)algebra and Curry-Howard Isomorphism,
    currently studying Homotopy Type Theory and Cubical Type Theory,
    familiar with Idris, Agda (\textbf{1 years} of experience,
    developer team member) and F$\star$
    \subitem Source code studied: Agda, Idris, miniagda, Mini-TT.

  \item \textbf{JetBrains MPS}:
    \textbf{1 years} of experience,
    understand concepts and usages of \textbf{Language-Oriented Programming}.

  \item \textbf{IDE Toolings}:
    \textbf{2 years} of experience,
    familiar with the IntelliJ Platform infrastructure and overall
    architecture (created the
    \href{https://plugins.jetbrains.com/plugin/10413-julia}
         {Julia plugin} and many others), also have experience with Eclipse/SonarQube.

  % platforms I am familiar with
  \item \textbf{Mobile Development}:
    \textbf{2 years} of experience,
    Android (Java, Kotlin (Anko)), Fuchsia (Flutter).

  \item \textbf{Developing Tools}:
    can adapt to any editors/OSs, usually use JetBrains IDEs and Emacs under Ubuntu,
    have experience with team tools like YouTrack, Jira, GitHub, BitBucket, Coding.net, Tower.
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.25ex]
  \item Blog: \url{https://ice1000.org/} partially translated into English
  \item Literate Agda Blog: \url{https://ice1000.org/lagda/} used Literate mode of Agda improved by me
  \item Bintray: \url{https://bintray.com/ice1000} published some useful JVM libraries
  \item IntelliJ Plugin developer: \url{https://plugins.jetbrains.com/author/10a216dd-c558-4aaf-aa8a-723f431452fb}
  \item Books about formal verification I've written: \url{https://github.com/ice1000/Books}
  \item Languages: English - fluent (TOEFL 100), Chinese - native speaker
  \item Opensource contributions: \url{https://ice1000.org/opensource-contributions/} \\
    pull-requested (functional improvements) to organizations like \textit{Microsoft, JetBrains, Ruby, Dropbox, PingCAP, TiKV},
    projects like \textit{agda, imgui, shields.io, intellij-solidity, IntelliJ-EmmyLua, intellij-haskell}
  \item StackOverflow: \url{https://stackoverflow.com/users/7083401/}
    3000+ reputations, also active on \href{https://stackexchange.com/users/9532102/} {other StackExchange} sites
  % https://raw.githubusercontent.com/ice1000/resume/master/resume.pdf
  \item Get the newest version of this resume: \url{https://tinyurl.com/y8xdlfug}
  \item \textbf{1 kyu} on
    \href{https://www.codewars.com/users/ice1000} {CodeWars},
    ranked \#37 on the whole site, primarily in Haskell
  \item Love making friends
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}

